
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex, colorlinks=true, urlcolor=blue, linkcolor=blue]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{p{0.72\textwidth}@{\extracolsep{\fill}}r}
      \hspace{-10pt} \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{p{0.72\textwidth}@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingFullSubtitle}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{p{0.72\textwidth}@{\extracolsep{\fill}}r}
      \hspace{-10pt} \textbf{#1} & #2 \\
      \multicolumn{2}{l}{\textit{\small#3}} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large William Beckman} & Email : \href{mailto:will@willbeckman.com}{will@willbeckman.com}\\
  \href{http://willbeckman.com/}{willbeckman.com} & Mobile : +1-410-236-7933 \\
  \href{https://www.linkedin.com/in/willbeckman/}{linkedin.com/in/willbeckman} & U.S. Citizen \\[4pt]
\end{tabular*}
\textit{Senior Machine Learning Engineer specializing in applied ML with AB-tested product impact.}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Master of Science in Computer Science - Specialization in Machine Learning; GPA: \textnormal{3.9}}{Aug 2018 -- Dec 2021}
      \resumeSubSubheading
      {Relevant coursework: Machine Learning, Reinforcement Learning, Deep Learning}{}
    \resumeSubheading
      {University of Maryland, College Park}{College Park, MD}
      {Bachelor of Science in Computer Science}{Aug 2012 -- May 2016}

  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Etsy}{Jun 2024 -- Present}
      {Senior Machine Learning Engineer, Ads Search Quality (Ranking \& Retrieval)}{Jan 2025 -- Present}

      \resumeItemListStart
        \resumeItem{PyTorch Ranking Model Migration}
          {Core contributor to the migration of the second-pass ads ranking model from TensorFlow to PyTorch; built the lifecycle management system for non-weight model state.
          \begin{itemize}
            \item \small{Ramped up on \textbf{+2.92\% Ads GMS} and \textbf{$\sim$\$1M/yr} in infrastructure serving cost savings.}
            \item \small{Migrated training from Beam/Dataflow + Vertex AI to Ray: \textbf{2--3x} faster training, GPU utilization $\sim$60\% $\rightarrow$ \textbf{$\sim$95\%}, preprocessing and evaluation runtimes reduced by \textbf{60\%}.}
          \end{itemize}}
        \resumeItem{Neural Information Retrieval (NIR) Embedding Model}
          {Migrated ads retrieval to a neural query-to-listing embedding model, ramping up on \textbf{+1.04\% Ads GMS} and \textbf{+\$4.21M} annualized sitewide GMS.}
        \resumeItem{Retrieval Candidate Blending}
          {Redesigned retrieval blending from greedy to round-robin and doubled candidates sent to the second-pass ranker, resulting in \textbf{+\$4.21M} annualized GMS, \textbf{+0.61\%} Ads CVR, and \textbf{+0.26\%} sitewide CVR.}
        \resumeItem{Semantic Relevance Filtering}
          {Added a semantic relevance filter in the retrieval layer to suppress low-relevance ad listings. Achieved \textbf{+\$4.98M} sitewide GMS with neutral Ads GMS impact; reduced first-page ad irrelevance from $\sim$7\% to \textbf{$<$5\%} as measured by an LLM teacher model, meeting the team's product quality goal.}
        \resumeItem{Solr Minimum Match Strictness}
          {Tightened Solr minimum keyword match to 100\% for short queries ($\leq$3 terms), up from $\sim$60\%. Despite reducing ads click revenue, the relevance improvement drove \textbf{+1.33\% Ads GMS}, \textbf{+1.55\% Ads CVR}, and \textbf{+\$1.9M} sitewide GMS.}
      \resumeItemListEnd


    \resumeSubSubheading
      {Machine Learning Engineer, Contractor}{Jun 2024 -- Dec 2024}
    \vspace{5pt}

    \resumeSubheadingFullSubtitle
      {Sabbatical}{Apr 2022 -- May 2024}
      {Completed a thru-hike of the 2,194.3-mile Appalachian Trail; pursued independent study and personal projects.}

    \vspace{5pt}
    \resumeSubheading
      {Capital One}{Jul 2016 -- Mar 2022}
      {Senior Machine Learning Engineer}{Feb 2019 -- Mar 2022}

      \resumeItemListStart
        \resumeItem{Fraud Detection Models}
          {Developed and productionized multiple ML models for credit card fraud detection, including a graph-based ring fraud algorithm ($\sim$\$10M/yr incremental savings), a third-party account takeover model ($>$\$15M/yr in savings), and a risky merchant classifier (\$5--10M/yr estimated savings).}
      \resumeItemListEnd

    \resumeSubSubheading
      {Software Engineer}{Feb 2018 -- Feb 2019}

      \resumeItemListStart
        \resumeItem{Corporate Strategy Data Pipeline}
          {Built Spark/Scala pipelines processing 100s of GBs of credit bureau data for the Corporate Strategy division.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Associate Software Engineer}{Jul 2016 -- Feb 2018}

      \resumeItemListStart
        \resumeItem{AWS Network Debugger}
          {Built a Boto3 CLI tool for diagnosing AWS network connectivity issues; adopted company-wide by staff architects.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Software/Infrastructure}{: Python, Ray, AWS, GCP, Docker, Airflow, git, Scala}
     \hfill \\
     \textbf{ML/Data}{: PyTorch, pyspark, SQL, pandas, numpy, scikit-learn, Databricks, Snowflake, BigQuery}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
